%
\newglossaryentry{API}{
	name=API, 
	description={The application programming interface describes how to interact with a system. The interface provides methodes which can be accessed from outside the system.}
}
%
\newglossaryentry{administrator}
{
	name=administrator,
	description={(Admin) Human individual, who monitors the system and controls user activities
}
}
%
\newglossaryentry{anonymous user}
{
	name=anonymous user,
	description={User, who isn't registered in the system}
}
%
\newglossaryentry{Tomcat}
{
	name=Apache Tomcat,
	description={Open source servlet container and http web server}
}
%
\newglossaryentry{arff}
{
	name=arff,
	description={Attribute-Relation File Format - ASCII format used for machine learning}
}
%
\newglossaryentry{browser}
{
	name=browser,
	description={Web-Browser - Software application for presenting/traversing informations in web; common browsers: Internet Explorer(IE), Firefox, Chrome, Safari, Opera}
}
%
\newglossaryentry{csv}
{
	name=csv,
	description={Comma-separated values(csv): file format, which stores tabular data in plain text}
}
%
\newglossaryentry{database}
{
	name=database,
	description={organized collection of data}
}
%
\newglossaryentry{Interface}
{
	name=Interface,
	description={Point of interaction between the application and any other entity}
}
%
\newglossaryentry{Java}
{
	name=Java,
	description={Concurrent, object-oriented programming language}
}
%
\newglossaryentry{Java EE}
{
	name=Java EE,
	description={Java Enterprise Edition (Java EE): collection of technologies and APIs for the Java platform to support "Enterprise" applications}
}
%
\newglossaryentry{Query}
{
	name=Query,
	description={In this document, query is called the process influenced by a user: from uploading data to the start of a specific algorithm }
}
%
\newglossaryentry{RDF}
{
	name=RDF,
	description={Resource Description Framework (RDF): data model based on the idea of making statements about resources in form of subject-predicate-object expressions }
}
%
\newglossaryentry{REST}
{
	name=REST,
	description={Representational State Transfer (REST): software architectural style of the world wide web using resources identified by URI, which can be operated upon using standard verbs}
}
%
\newglossaryentry{Servlet}
{
	name=Servlet,
	description={An object(class instance), which is able to receive and to response requests}
}
%
\newglossaryentry{User}
{
	name=User,
	description={A human individual, who's using the system}
} 
%
\newglossaryentry{HTTPS}
{
	name=HTTPS,
	description={Hypertext Transfer Protocoll Secure (HTTPS): Descriptionprotocol for secure communication over a computer network
}
} 
\newglossaryentry{test data}
{name=test data,
description={A test-data or training set is a set of data used to discover potentially predictive relationships. A test set is a set of data used to assess the strength and utility of a predictive relationship.}
} 
\newglossaryentry{ASCII}
{
	name=ASCII,
	description={American Standard Code for Information Interchange (ASCII) is a character-encoding scheme. ASCII codes represent text in computers, communications equipment, and other devices that use text.}
} 
\newglossaryentry{ID}
{
	name=ID,
	description={(Identification) Is a unique number that is used to identify a specific object
}
}
\newglossaryentry{web-app}
{
	name=web-app,
	description={A web application (web-app) is a client-server software application in which the client (or user interface) runs in a web browser. 
}
}
\newglossaryentry{framework}
{
	name=framework,
	description={A software framework is an abstraction in which software providing generic functionality can be selectively changed by additional user-written code, thus providing application-specific software.}
}
\newglossaryentry{Linux}
{
	name=Linux,
	description={Linux is a Unix-like computer operating system (OS) assembled under the model of free and open-source software development and distribution.}
}
\newglossaryentry{Mac}
{
	name=Mac,
	description={A computer operating system (OS)}
}
\newglossaryentry{Windows}
{
	name=Windows,
	description={A computer operating system (OS)}
}
\newglossaryentry{RAM}
{
	name=RAM,
	description={Random-access memory (RAM) is a form of computer data storage}
}
\newglossaryentry{SMO}
{
	name=SMO,
	description={A Data-Mining algorithm}
}
\newglossaryentry{J48}
{
	name=J48,
	description={J48 is an open source Java implementation of the C4.5 algorithm in the weka data mining tool.}
}
\newglossaryentry{Random Forest}
{
	name=Random Forest,
	description={Random forests are an ensemble learning method for classification, regression and other tasks, that operate by constructing a multitude of decision trees at training time and outputting the class that is the mode of the classes (classification) or mean prediction (regression) of the individual trees. Random forests correct for decision trees' habit of overfitting to their training set.}
}
\newglossaryentry{jar}
{
	name=jar,
	description={Java Archive is a package file format typically used to aggregate many Java class files and associated metadata and resources (text, images, etc.) into one file to distribute application software or libraries on the Java platform.}
}
\newglossaryentry{EULA}
{
	name=EULA,
	description={An end-user license agreement (EULA) or software license agreement is the contract between the licensor and purchaser, establishing the purchaser's right to use the software.}
}
\newglossaryentry{SPARQL}
{
	name=SPARQL,
	description={Protocol and RDF Query Language: RDF query language for databases, able to retrieve and manipulate data stored in RDF format }
}
\newglossaryentry{IEEE}
{
	name=IEEE,
	description={IEEE stands for the "Institute of Electrical and Electronics Engineers".}
}
\newglossaryentry{WEKA}
{
	name=weka,
	description={Suite of machine learning software, which contains a collection of tools and algorithms for data analysis.}
}
\newglossaryentry{Model}
{
	name=Model,
	description={A -statistical- model embodies a set of assumptions concerning the generation of the observed data, and similar data from a larger population. A model represents, often in considerably idealized form, the data-generating process.}
}